Higgs Assisted Razor Search for Higgsinos at 100 TeV

### 2019-07-23 main.tex
removing abs value bars around mu in dm contour plot
Updates from Overleaf

\begin{figure}[h]
  \centering
  \includegraphics[width=0.49\textwidth]{images/xsection_plot.pdf}
  \includegraphics[width=0.49\textwidth]{images/br_plot.pdf}
  \caption{Higgsino pair production $\N_2\N_3$
    cross section (left panel), calculated using
    Prospino2~\cite{Beenakker:1999xh},  and decay branching fractions
    (right panel), calculated in SUSY-HIT~\cite{Djouadi:2006bz},  as a function
    of $\mu$ for $M_1=25$ GeV. However, it should be noted that the dependence
    on $M_1$ is very weak.  \Shufang{Could you use $\mu$ for both xlabels?  The
    CS and Br will depend slightly on the sign of mu.  Since we do use positive
  mu in our analyses, let's label it this way.  I have a footnote in intro to
explain the sign effect of mu.  Also, change right panel, ylabel to be either
Br or Branching Fraction.}
}
  \label{fig:xsection_plot}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=0.49\textwidth]{images/xsection_plot.pdf}
  \includegraphics[width=0.49\textwidth]{images/br_plot.pdf}
  \caption{Higgsino pair production $\N_2\N_3$
    cross section (left panel), calculated using
    Prospino2~\cite{Beenakker:1999xh},  and decay branching fractions
    (right panel), calculated in SUSY-HIT~\cite{Djouadi:2006bz},  as a function
    of $\mu$ for $M_1=25$ GeV. However, it should be noted that the dependence
    on $M_1$ is very weak.
}
  \label{fig:xsection_plot}
\end{figure}
